---
title: "TidyTemplate"
date: 2021-07-23
output: html_document
---

```{r setup}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(here)
library(geofacet)
library(lubridate)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-07-20")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)
```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

tidy_data <- tt$drought %>%
  arrange(map_date) %>%
  mutate(drought_lvl = if_else(drought_lvl != "None",
    "Some level of drought",
    drought_lvl
  )) %>%
  group_by(
    map_date,
    state_abb,
    drought_lvl
  ) %>%
  summarise(pct_pop = sum(pop_pct)) %>%
  ungroup() %>%
  mutate(map_date = ymd(map_date))
```

# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

tidy_data %>%
  filter(drought_lvl == "Some level of drought") %>%
  ggplot(aes(
    x = map_date,
    y = pct_pop
  )) +
  geom_line(color = "#BA4A00") +
  facet_geo(~state_abb) +
  theme_bw() +
  theme(
    axis.text.x = element_text(size = 6),
    axis.text.y = element_text(size = 6)
  ) +
  labs(
    y = "Porcentaje",
    x = "",
    title = "Porcentaje de poblacion afectada por algún tipo de sequía",
    subtitle = "en EEUU, 2001-07 a 2021-07",
    caption = "Fuente:  U.S. Drought Monitor"
  )

  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = here("2021-07-20_tidytuesday",
                  "2021-07-20_tidytuesday.png"),
  device = "png",
  width = 13,
  height = 9)

```
